\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2020-09-02 popl-2019-journal-v/appendix.tex
port to JFP latex template.

\section{\trgcm{} instruction interpretation}
\label{app:instr-interpretation}
In this section, we present the interpretation of the \trgcm{} instructions left out of \figurename~\ref{fig:target-op-sem}.

@@

\section{\srccm{} instruction interpretation}
In this section, we present the interpretation of the \srccm{} instructions left out of \figurename~\ref{fig:target-op-sem}.
For the instructions that only change slightly on \srccm{} compared to \trgcm{}, we include the \srccm{} specific things in blue and the things both have in common in black.

>>>>

\section{\trgcm{} instruction interpretation}
\label{app:instr-interpretation}
In this section, we present the interpretation of the \trgcm{} instructions left out of Figure~\ref{fig:target-op-sem1} and~\ref{fig:target-op-sem2}.

@@

\section{\srccm{} instruction interpretation}
In this section, we present the interpretation of the \srccm{} instructions left out of Figure~\ref{fig:target-op-sem1} and~\ref{fig:target-op-sem2}.
For the instructions that only change slightly on \srccm{} compared to \trgcm{}, we include the \srccm{} specific things in blue and the things both have in common in black.
